An Invariant Framework for Conducting Reproducible Computational Science

### 2015-03-31 observation.tex
some small changes to observation.tex
stylistic again

\item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, these applications depend on a large number of external and local dependencies.
External dependencies are often explicitly stated, such as when the application makes connections to Github resources or CVS servers for downloading source files. 
When the application has initiated execution then implicit network connections may be present that require identification of dependencies on all machines where execution takes place. 
Implicit local dependencies can arise as a result of mounted filesystems. In \emph{TauRoast}, the application data and code is distributed on five networked filesystems, and in \emph{Athena} on two networked filesystems. 
Since these filesystems appear local to the application machine, it is important to check and capture mounted filesystems and their respective mount points.

>>>>

\item {\bf Identifying all dependencies.}  Due to the distributed, collaborative nature of HEP software development, these applications depend on a large number of external and local software components.
External dependencies are often explicitly stated, such as when the application makes connections to Github resources or CVS servers for downloading source files. 
When the application has initiated execution then implicit network connections may be present that require identification of dependencies on all machines where execution takes place. 
Implicit local dependencies can arise as a result of mounted filesystems. In \emph{TauRoast}, the application data and code is distributed on five networked filesystems, and in \emph{Athena} on two networked filesystems. 
Since these filesystems appear local to the application machine, it is important to check and capture mounted filesystems and their respective mount points.
